|

### 2021-02-04 appendix/appendix.Rmd
reorder factors exp01, add code exp02

@@

@@

@@

@@

@@

@@

@@

\footnotesize
```{r race, warning=F, error=F, cache=T}
df1 %>%
  group_by(race) %>%
  filter(!is.na(race)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  rename(Race = race) %>%
  kbl(., booktabs = TRUE,  linesep = "",
      caption = "Race") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

@@

As expected, our sample is also more educated than [the Brazilian
population](https://educa.ibge.gov.br/jovens/conheca-o-brasil/populacao/18317-educacao.html).
About `r df2[1, 3]*100`% of the respondents have a college degree, and `r df2[3, 3]`%
have graduate school education.

@@

In terms of household income, `r df2[6, 3]*100`% of the respondents earns from
R\$5,0001 to R\$10,000 per month (US\$915 to US\$1830 as of January 2021), which
comprise the largest group in our sample. However, the sample also contains
`r df2[2, 3]*100`% of participants whose household income ranges between R\$1,001
and R\$2,000 (US\$ 184 to US\$368) and `r df2[7, 3]*100`% with household incomes
up to R\$1,000, which is roughly equivalent to Brazil's monthly minimum wage. In
this respect, we have reached participants from all social classes.

@@

We have also collected information regarding the subjects' political ideology.
Most respondents identify themselves as right-wingers (`r df2[7, 3]*100`%),
followed by left-wingers (`r df2[5, 3]*100`%), and centrists (`r df2[1, 3]*100`%).
Subjects who do not know their ideology or prefer not to tell their
political beliefs are also large in number (`r df2[4, 3]*100`% and
`r df2[6, 3]*100`%, respectively).

@@

\footnotesize
```{r conjoint-education, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.7, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  drop_na(education) %>%
  filter(education == c("College", "Graduate School",
                        "Primary School", "Secondary School",
                        "High School")) %>%
  mutate(education2 = case_when(education == "Primary School" ~ "Primary or Secondary School",
                                education == "Secondary School" ~ "Primary or Secondary School",
                                TRUE ~ education))
cjdt$Education <- factor(cjdt$education2)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Education)

@@

# Tables
mm_college <- mm_by %>% filter(BY == "College")
table_mm_by(mm_college, capt = "Marginal Means -- College Degree")
mm_grad <- mm_by %>% filter(BY == "Graduate School")
table_mm_by(mm_grad, capt = "Marginal Means -- Graduate School Degree")
mm_high <- mm_by %>% filter(BY == "High School")
table_mm_by(mm_high, capt = "Marginal Means -- High School Degree")
mm_pri_sec <- mm_by %>% filter(BY == "Primary or Secondary School")
table_mm_by(mm_pri_sec, capt = "Marginal Means -- Primary or Secondary School Degree")
```
\normalsize

@@

\footnotesize
```{r conjoint-income, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.7, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  drop_na(household_income) %>%
  mutate(household_income2 = case_when(household_income == "Up to R$1,000" ~ "Up to R$3,000",
                                       household_income == "From R$1,001 to R$2,000" ~ "Up to R$3,000",
                                       household_income == "From R$2,001 to R$3,000" ~ "Up to R$3,000",
                                       household_income == "From R$3,001 to R$5,000" ~ "From R$3,001 to R$5,000",
                                       household_income == "From R$5,001 to R$10,000" ~ "Above R$5,000",
                                       household_income == "From R$10,001 to R$20,000" ~ "Above R$5,000",
                                       household_income == "Above R$20,000" ~ "Above R$5,000",
                                       TRUE ~ NA_character_))
cjdt$Income <- factor(cjdt$household_income2)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Income)

@@

\footnotesize
```{r conjoint-penalty, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.3, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  drop_na(death_penalty)
cjdt$Death_Penalty <- factor(cjdt$death_penalty)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Death_Penalty)

@@

# Tables
mm_dk <- mm_by %>% filter(BY == "Don't Know")
table_mm_by(mm_dk, capt = "Marginal Means -- Support for Death Penalty: Do Not Know")
mm_no <- mm_by %>% filter(BY == "No")
table_mm_by(mm_no, capt = "Marginal Means -- Support for Death Penalty: No")
mm_rns <- mm_by %>% filter(BY == "Rather Not Say")
table_mm_by(mm_rns, capt = "Marginal Means -- Support for Death Penalty: Rather Not Say")
mm_yes <- mm_by %>% filter(BY == "Yes")
table_mm_by(mm_yes, capt = "Marginal Means -- Support for Death Penalty: Yes")
```
\normalsize

@@

\footnotesize
```{r conjoint-victimization, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.6, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id")
cjdt$Previous_Victim <- factor(cjdt$previous_victim_dummy)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Previous_Victim)

@@

# Tables
mm_no <- mm_by %>% filter(BY == "No")
table_mm_by(mm_no, capt = "Marginal Means -- Previous Victimization (12 Months): No")
mm_yes <- mm_by %>% filter(BY == "Yes")
table_mm_by(mm_yes, capt = "Marginal Means -- Previous Victimization (12 Months): Yes")
```
\normalsize

@@

\footnotesize
```{r conjoint-policing, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.7, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  mutate(views_police2 = case_when(views_police == "Rather Not Say" ~ NA_character_,
                                   views_police == "Don't Know" ~ NA_character_,
                                   TRUE ~ views_police)) %>% drop_na(views_police2)
cjdt$Police <- factor(cjdt$views_police2)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Police)

@@

# Tables
mm_bad <- mm_by %>% filter(BY == "Bad")
table_mm_by(mm_bad, capt = "Marginal Means -- Opinion on the Police: Bad")
mm_good <- mm_by %>% filter(BY == "Good")
table_mm_by(mm_good, capt = "Marginal Means -- Opinion on the Police: Good")
mm_regular <- mm_by %>% filter(BY == "Regular")
table_mm_by(mm_regular, capt = "Marginal Means -- Opinion on the Police: Regular")
mm_vbad <- mm_by %>% filter(BY == "Very Bad")
table_mm_by(mm_vbad, capt = "Marginal Means -- Opinion on the Police: Very Bad")
mm_vgood <- mm_by %>% filter(BY == "Very Good")
table_mm_by(mm_vgood, capt = "Marginal Means -- Opinion on the Police: Very Good")
```
\normalsize

@@

\footnotesize
```{r conjoint-justice, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.6, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  mutate(views_justice2 = case_when(views_justice == "Rather Not Say" ~ NA_character_,
                                    views_justice == "Don't Know" ~ NA_character_,
                                   TRUE ~ views_justice)) %>% drop_na(views_justice2)
cjdt$Judiciary <- factor(cjdt$views_justice2)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Judiciary)

@@

# Tables
mm_bad <- mm_by %>% filter(BY == "Bad")
table_mm_by(mm_bad, capt = "Marginal Means -- Opinion on the Judicial System: Bad")
mm_good <- mm_by %>% filter(BY == "Good")
table_mm_by(mm_good, capt = "Marginal Means -- Opinion on the Judicial System: Good")
mm_regular <- mm_by %>% filter(BY == "Regular")
table_mm_by(mm_regular, capt = "Marginal Means -- Opinion on the Judicial System: Regular")
mm_vbad <- mm_by %>% filter(BY == "Very Bad")
table_mm_by(mm_vbad, capt = "Marginal Means -- Opinion on the Judicial System: Very Bad")
mm_vgood <- mm_by %>% filter(BY == "Very Good")
table_mm_by(mm_vgood, capt = "Marginal Means -- Opinion on the Judicial System: Very Good")
```
\normalsize

@@

Table \ref{tab:exp02main} summarizes our results.

@@

m1 <- lm(exp02_outcomes ~ exp02_police_treat, data = df_exp02)
m1cov <- coeftest(m1, vcov = vcovHC(m1, type = "HC2"))
m1se <- sqrt(diag(m1cov))

m2 <- lm(exp02_outcomes ~ exp02_slow_justice_treat, data = df_exp02)
m2cov <- coeftest(m2, vcov = vcovHC(m2, type = "HC2"))
m2se <- sqrt(diag(m2cov))

m3 <- lm(exp02_outcomes ~ exp02_small_punishment_treat, data = df_exp02)
m3cov <- coeftest(m3, vcov = vcovHC(m3, type = "HC2"))
m3se <- sqrt(diag(m3cov))

m4 <- lm(exp02_outcomes ~ exp02_any_treat, data = df_exp02)
m4cov <- coeftest(m4, vcov = vcovHC(m4, type = "HC2"))
m4se <- sqrt(diag(m4cov))

stargazer(m1, m2, m3, m4, se = list(m1se, m2se, m3se, m4se), header = FALSE,
title = "Experiment 02 -- Main Results", align = TRUE, label = "tab:exp02main",
dep.var.caption = "\\textit{Dependent Variable}", dep.var.labels = "Lynching Support",
covariate.labels = c("Police does not patrol area", "Justice too slow",
"Punishment not harsh enough", "Combined treatments"),
column.sep.width = "3pt", notes = "Robust standard error in parentheses.",
keep.stat = c("n", "rsq"), no.space = TRUE)
```
\normalsize

>>>>

         race = fct_relevel(race, "Other", "Rather Not Say", after = Inf),

@@

         education = fct_relevel(education, "Primary School", "Secondary School", "High School",
                                 "College", "Graduate School", "Don't Know"),

@@

         household_income = fct_relevel(household_income, "Up to R$1,000",
                                        "From R$1,001 to R$2,000", "From R$2,001 to R$3,000",
                                        "From R$3,001 to R$5,000", "From R$5,001 to R$10,000",
                                        "From R$10,001 to R$20,000", "Above R$20,000"),

@@

         ideology = fct_relevel(ideology, "Left", "Center-Left", "Center",
                                "Center-Right", "Right", "Don't Know",
                                "Rather Not Say"),

@@

         death_penalty = fct_relevel(death_penalty, "Don't Know",
                                     "Rather Not Say", after = Inf),

@@

         views_police = fct_relevel(views_police, "Very Good", "Good", "Regular",
                                    "Bad", "Very Bad", "Don't Know", "Rather Not Say"),

@@

         views_justice = fct_relevel(views_justice, "Very Good", "Good", "Regular",
                                    "Bad", "Very Bad", "Don't Know", "Rather Not Say"),

@@

\footnotesize
```{r race, warning=F, error=F, cache=T}
df1 %>%
  group_by(race) %>%
  filter(!is.na(race)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  rename(Race = race) %>%
  mutate(Race = fct_relevel(Race, "Other", "Rather Not Say", after = Inf)) %>%
  kbl(., booktabs = TRUE,  linesep = "",
      caption = "Race") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

@@

As expected, our sample is also more educated than [the Brazilian
population](https://educa.ibge.gov.br/jovens/conheca-o-brasil/populacao/18317-educacao.html).
About `r df2[4, 3]*100`% of the respondents have a college degree, and `r df2[5, 3]`%
have graduate school education.

@@

In terms of household income, `r df2[5, 3]*100`% of the respondents earn from
R\$5,0001 to R\$10,000 per month (US\$915 to US\$1830 as of January 2021), which
comprise the largest group in our sample. However, the sample also contains
`r df2[2, 3]*100`% of participants whose household income ranges between R\$1,001
and R\$2,000 (US\$ 184 to US\$368) and `r df2[1, 3]*100`% with household incomes
up to R\$1,000, which is roughly equivalent to Brazil's monthly minimum wage. In
this respect, we have reached participants from all social classes.

@@

We have also collected information regarding the subjects' political ideology.
Most respondents identify themselves as right-wingers (`r df2[5, 3]*100`%),
followed by left-wingers (`r df2[1, 3]*100`%), and centrists (`r df2[3, 3]*100`%).
Subjects who do not know their ideology or prefer not to tell their
political beliefs are also large in number (`r df2[6, 3]*100`% and
`r df2[7, 3]*100`%, respectively).

@@

\footnotesize
```{r conjoint-education, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=6, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  drop_na(education) %>%
  filter(education == c("College", "Graduate School",
                        "Primary School", "Secondary School",
                        "High School")) %>%
  mutate(education2 = case_when(education == "Primary School" ~ "Primary or Secondary School",
                                education == "Secondary School" ~ "Primary or Secondary School",
                                TRUE ~ education),
         education2 = fct_relevel(education2, "Primary or Secondary School",
                                  "High School", "College", "Graduate School"))
cjdt$Education <- factor(cjdt$education2)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Education)

@@

# Tables
mm_pri_sec <- mm_by %>% filter(BY == "Primary or Secondary School")
table_mm_by(mm_pri_sec, capt = "Marginal Means -- Primary or Secondary School Degree")
mm_high <- mm_by %>% filter(BY == "High School")
table_mm_by(mm_high, capt = "Marginal Means -- High School Degree")
mm_college <- mm_by %>% filter(BY == "College")
table_mm_by(mm_college, capt = "Marginal Means -- College Degree")
mm_grad <- mm_by %>% filter(BY == "Graduate School")
table_mm_by(mm_grad, capt = "Marginal Means -- Graduate School Degree")
```
\normalsize

@@

\footnotesize
```{r conjoint-income, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=6, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  drop_na(household_income) %>%
  mutate(household_income2 = case_when(household_income == "Up to R$1,000" ~ "Up to R$3,000",
                                       household_income == "From R$1,001 to R$2,000" ~ "Up to R$3,000",
                                       household_income == "From R$2,001 to R$3,000" ~ "Up to R$3,000",
                                       household_income == "From R$3,001 to R$5,000" ~ "From R$3,001 to R$5,000",
                                       household_income == "From R$5,001 to R$10,000" ~ "Above R$5,000",
                                       household_income == "From R$10,001 to R$20,000" ~ "Above R$5,000",
                                       household_income == "Above R$20,000" ~ "Above R$5,000",
                                       TRUE ~ NA_character_),
         household_income2 = fct_relevel(household_income2, "Up to R$3,000", "From R$3,001 to R$5,000",
                                         "Above R$5,000"))
cjdt$Income <- factor(cjdt$household_income2)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Income)

@@

\footnotesize
```{r conjoint-penalty, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.3, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  drop_na(death_penalty) %>%
  mutate(death_penalty = fct_relevel(death_penalty, "Yes", "No",
                                     "Don't Know", "Rather Not Say"))
cjdt$Death_Penalty <- factor(cjdt$death_penalty)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Death_Penalty)

@@

# Tables
mm_yes <- mm_by %>% filter(BY == "Yes")
table_mm_by(mm_yes, capt = "Marginal Means -- Support for Death Penalty: Yes")
mm_no <- mm_by %>% filter(BY == "No")
table_mm_by(mm_no, capt = "Marginal Means -- Support for Death Penalty: No")
mm_dk <- mm_by %>% filter(BY == "Don't Know")
table_mm_by(mm_dk, capt = "Marginal Means -- Support for Death Penalty: Do Not Know")
mm_rns <- mm_by %>% filter(BY == "Rather Not Say")
table_mm_by(mm_rns, capt = "Marginal Means -- Support for Death Penalty: Rather Not Say")
```
\normalsize

@@

\footnotesize
```{r conjoint-victimization, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.6, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  mutate(previous_victim_dummy, "Yes", "No")
cjdt$Previous_Victim <- factor(cjdt$previous_victim_dummy)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Previous_Victim)

@@

# Tables
mm_yes <- mm_by %>% filter(BY == "Yes")
table_mm_by(mm_yes, capt = "Marginal Means -- Previous Victimization (12 Months): Yes")
mm_no <- mm_by %>% filter(BY == "No")
table_mm_by(mm_no, capt = "Marginal Means -- Previous Victimization (12 Months): No")
```
\normalsize

@@

\footnotesize
```{r conjoint-policing, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=6, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  mutate(views_police2 = case_when(views_police == "Rather Not Say" ~ NA_character_,
                                   views_police == "Don't Know" ~ NA_character_,
                                   TRUE ~ views_police),
         views_police2 = fct_relevel(views_police2, "Very Good", "Good",
                                     "Regular", "Bad", "Very Bad")) %>%
  drop_na(views_police2)
cjdt$Police <- factor(cjdt$views_police2)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Police)

@@

# Tables
mm_vgood <- mm_by %>% filter(BY == "Very Good")
table_mm_by(mm_vgood, capt = "Marginal Means -- Opinion on the Police: Very Good")
mm_good <- mm_by %>% filter(BY == "Good")
table_mm_by(mm_good, capt = "Marginal Means -- Opinion on the Police: Good")
mm_regular <- mm_by %>% filter(BY == "Regular")
table_mm_by(mm_regular, capt = "Marginal Means -- Opinion on the Police: Regular")
mm_bad <- mm_by %>% filter(BY == "Bad")
table_mm_by(mm_bad, capt = "Marginal Means -- Opinion on the Police: Bad")
mm_vbad <- mm_by %>% filter(BY == "Very Bad")
table_mm_by(mm_vbad, capt = "Marginal Means -- Opinion on the Police: Very Bad")
```
\normalsize

@@

\footnotesize
```{r conjoint-justice, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=5.6, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  mutate(views_justice2 = case_when(views_justice == "Rather Not Say" ~ NA_character_,
                                    views_justice == "Don't Know" ~ NA_character_,
                                   TRUE ~ views_justice),
         views_justice2 = fct_relevel(views_justice2, "Very Good", "Good",
                                      "Regular", "Bad", "Very Bad")) %>%
  drop_na(views_justice2)
cjdt$Judiciary <- factor(cjdt$views_justice2)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Judiciary)

@@

# Tables
mm_vgood <- mm_by %>% filter(BY == "Very Good")
table_mm_by(mm_vgood, capt = "Marginal Means -- Opinion on the Judicial System: Very Good")
mm_good <- mm_by %>% filter(BY == "Good")
table_mm_by(mm_good, capt = "Marginal Means -- Opinion on the Judicial System: Good")
mm_regular <- mm_by %>% filter(BY == "Regular")
table_mm_by(mm_regular, capt = "Marginal Means -- Opinion on the Judicial System: Regular")
mm_bad <- mm_by %>% filter(BY == "Bad")
table_mm_by(mm_bad, capt = "Marginal Means -- Opinion on the Judicial System: Bad")
mm_vbad <- mm_by %>% filter(BY == "Very Bad")
table_mm_by(mm_vbad, capt = "Marginal Means -- Opinion on the Judicial System: Very Bad")
```
\normalsize

@@

Table \ref{tab:exp02main} summarizes our results. As we see, none of the
treatment effects are statistically significant at conventional levels. This
indicates that institutional factors do not affect lynching support in our
sample.

@@

m1 <- lm(exp02_outcomes ~ exp02_police_treat, data = df_exp02)
m1cov <- coeftest(m1, vcov = vcovHC(m1, type = "HC1"))
m1se <- sqrt(diag(m1cov))

m2 <- lm(exp02_outcomes ~ exp02_slow_justice_treat, data = df_exp02)
m2cov <- coeftest(m2, vcov = vcovHC(m2, type = "HC1"))
m2se <- sqrt(diag(m2cov))

m3 <- lm(exp02_outcomes ~ exp02_small_punishment_treat, data = df_exp02)
m3cov <- coeftest(m3, vcov = vcovHC(m3, type = "HC1"))
m3se <- sqrt(diag(m3cov))

m4 <- lm(exp02_outcomes ~ exp02_any_treat, data = df_exp02)
m4cov <- coeftest(m4, vcov = vcovHC(m4, type = "HC1"))
m4se <- sqrt(diag(m4cov))

stargazer(m1, m2, m3, m4, se = list(m1se, m2se, m3se, m4se), header = FALSE,
          title = "Experiment 02 -- Main Results", align = TRUE, label = "tab:exp02main",
          dep.var.caption = "\\textit{Dependent Variable}", dep.var.labels = "Lynching Support",
          covariate.labels = c("Police does not patrol area", "Justice too slow",
                               "Punishment not harsh enough", "Combined treatments"),
          column.sep.width = "3pt", notes = "Robust standard error in parentheses.",
          keep.stat = c("n", "rsq"), no.space = TRUE, font.size = "footnotesize")
```
\normalsize

## Demographic Characteristics and Lynching Support

Here we evaluate the impact of individual characteristics on lynching support.
We combine all treatment and control groups and measure whether demographic
information, which we collected in our questionnaire, changes baseline levels.

```{r exp02-demographics, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
df_exp02_group <- df_exp02 %>%
  filter(gender == c("Female", "Male"),
         race %in% c("Asian", "Black", "Mixed Race", "White"),
         education %in% c("College", "Graduate School",
                          "Primary School", "Secondary School", "High School")) %>%
  mutate(education2 = case_when(education == "Primary School" ~ "Primary or Secondary School",
                                education == "Secondary School" ~ "Primary or Secondary School",
                                TRUE ~ as.character(education))) %>%
  mutate(household_income2 = case_when(household_income == "Up to R$1,000" ~ "Up to R$3,000",
                                       household_income == "From R$1,001 to R$2,000" ~ "Up to R$3,000",
                                       household_income == "From R$2,001 to R$3,000" ~ "Up to R$3,000",
                                       household_income == "From R$3,001 to R$5,000" ~ "From R$3,001 to R$5,000",
                                       household_income == "From R$5,001 to R$10,000" ~ "Above R$5,000",
                                       household_income == "From R$10,001 to R$20,000" ~ "Above R$5,000",
                                       household_income == "Above R$20,000" ~ "Above R$5,000",
                                       TRUE ~ NA_character_))

m1 <- lm(exp02_outcomes ~ gender, data = df_exp02_group)
m1cov <- coeftest(m1, vcov = vcovHC(m1, type = "HC1"))
m1se <- sqrt(diag(m1cov))

m2 <- lm(exp02_outcomes ~ age, data = df_exp02_group)
m2cov <- coeftest(m2, vcov = vcovHC(m2, type = "HC1"))
m2se <- sqrt(diag(m2cov))

m3 <- lm(exp02_outcomes ~ race, data = df_exp02_group)
m3cov <- coeftest(m3, vcov = vcovHC(m3, type = "HC1"))
m3se <- sqrt(diag(m3cov))

m4 <- lm(exp02_outcomes ~ education2, data = df_exp02_group)
m4cov <- coeftest(m4, vcov = vcovHC(m4, type = "HC1"))
m4se <- sqrt(diag(m4cov))

m5 <- lm(exp02_outcomes ~ household_income2, data = df_exp02_group)
m5cov <- coeftest(m5, vcov = vcovHC(m5, type = "HC1"))
m5se <- sqrt(diag(m5cov))

m6 <- lm(exp02_outcomes ~ ideology, data = df_exp02_group)
m6cov <- coeftest(m6, vcov = vcovHC(m6, type = "HC1"))
m6se <- sqrt(diag(m6cov))

m7 <- lm(exp02_outcomes ~ previous_victim_dummy, data = df_exp02_group)
m7cov <- coeftest(m7, vcov = vcovHC(m7, type = "HC1"))
m7se <- sqrt(diag(m7cov))

m8 <- lm(exp02_outcomes ~ views_police, data = df_exp02_group)
m8cov <- coeftest(m8, vcov = vcovHC(m8, type = "HC1"))
m8se <- sqrt(diag(m8cov))

m9 <- lm(exp02_outcomes ~ views_justice, data = df_exp02_group)
m9cov <- coeftest(m9, vcov = vcovHC(m9, type = "HC1"))
m9se <- sqrt(diag(m9cov))

stargazer(m1, m2, m3, m4, m5, se = list(m1se, m2se, m3se, m4se, m5se), header = FALSE,
          align = TRUE, label = "exp02demo1",
          title = "Experiment 02 -- Effect of Demographic Characteristics on Lynching Support", 
          dep.var.caption = "\\textit{Dependent Variable}", dep.var.labels = "Lynching Support",
          covariate.labels = c("Male", "Age (years)", "Black", "Mixed Race",
                               "White", "Graduate School", "High School",
                               "Primary or Secondary School", ""),
          column.sep.width = "3pt", notes = "Robust standard error in parentheses.",
          keep.stat = c("n", "rsq"), no.space = TRUE)

stargazer(m6, m7, m8, m9, se = list(m6se, m7se, m8se, m9se), header = FALSE,
          title = "Experiment 02 -- Effect of Demographic Characteristics on Lynching Support", 
dep.var.caption = "\\textit{Dependent Variable}", dep.var.labels = "Lynching Support",
column.sep.width = "3pt", notes = "Robust standard error in parentheses.",
keep.stat = c("n", "rsq"), no.space = TRUE)
```
